### 2014-02-02 thesis/src/chapters/chapter-design.tex
Thesis: add autonomic cloud instance manager
Thesis: added stack controller

% darek
\section{Autonomic stack manager}
\subsection{Managed resource}

>>>>

% darek
\section{Autonomic stack manager}
Autonomic stack manager is responsible for a management of a homogeneous resource - containers that together form a stack. More specifically, stack is subjected to:
\begin{inparaenum}[a)]
 \item monitoring its containers
 \item horizontal scaling
 \item changing applied load-balancing algorithms
 \item component replication
\end{inparaenum}

\subsection{Managed resource}
As it was stated in an overview, a stack is a group of containers configured to serve a common purpose (i.e. as a server cluster). In practise, this group consists of a master node and slaves: loadbalancer and java application workers or a master and slave databases, for example. Each stack type may leverage different mechanisms to enable that master-slave relation. Although specific decisions are left to an implementation, chapter X summarises common load-balancing mechanisms.

\subsubsection{Touchpoint}
Stack's touchpoint aims to provide information about the state and condition of a whole group of nodes: master as well as its slaves. As a consequence, from a structural perspective, it is decentralise and consists of a multiple agents. Key properties that should be manageable by a touch point include:
\begin{itemize}
 \item number of service requests passed to a master node
 \item cluster's response time
 \item average cpu / memory usage in cluster
 \item packet loss from all nodes
\end{itemize}

\subsection{Autonomic controller}

\subsubsection{Monitor}
During monitoring phase, controller gathers data from a multiple agents located in stacks' nodes: master and slaves. It is important to ensure that received data is synchronised in time, consequently it can be analysed collectively to find a symptoms covering all of the nodes.

\subsubsection{Analysis}
Analysis phase can be based on one of the models mentioned in an overview. Beside this, following stack and loadbalancing specific models can be taken into consideration:
\begin{asparaenum}
 \item[\textbf{Discrete event simulation model}] It evaluates different balancing algorithms (e.g. round robin, least connection, etc ) to predict which produces least Load-Balancing-Metric (LBM) and packet loss \cite{idziorek2010discrete}.
 \item[\textbf{Optimal static load balancing}] It aims to minimize mean response time of load distributed among servers \cite{tantawi1985optimal}. This model takes into account node's processing time as well as network delays - mean delay time is expressed as weighted sum of them.
 \item[\textbf{Power usage minimisation}] This model is focused on saving computing power by removing computing node when its resource are not necessary. Key assumption is that there is a very little difference in cost of keeping node alive and keeping it 100\% busy. As a consequence nodes should be shut down whenever it is possible \cite{pinheiro2001load}.
\end{asparaenum}

\subsubsection{Planning}
Plan module creates a sequence of changes enacting required QoS. Importantly, produced workflow should minimize or eliminate time during which stack becomes an unavailable due to incorporating additonal slaves or changing load-balancing mechanism, for instance. This can be done using redundant stack or its components to serve requests for a given period of time.

\subsubsection{Execution}
Stack autonomic controller executes actions such as:
\begin{itemize}
 \item horizontal scaling: adding slave nodes
 \item changing load-balancing algorithm
 \item changing network-topology to optimize time needed to reach a stack
 \item replicating master node and hence eliminating SPOF
\end{itemize}
